Log or not

### 2021-10-25 analysis/Analysis.Rmd
rerun plots with higher sample number

n <- 100
quantiles <- c(0.01, 0.025, seq(0.05, 0.95, by = 0.05), 0.975, 0.99)
rerun_simulation <- FALSE

@@

p1 <- plot_multiple(res, equal_means = TRUE, equal_vars = TRUE) 
ggsave(p1, filename = here("output", "effect_equal_mean_equal_var.png"))

p2 <- plot_multiple(res, equal_means = FALSE, equal_vars = TRUE) 
ggsave(p2, filename = here("output", "effect_unequal_mean_equal_var.png"))

p3 <- plot_multiple(res, equal_means = TRUE, equal_vars = FALSE) 
ggsave(p3, filename = here("output", "effect_equal_mean_unequal_var.png"))

p4 <- plot_multiple(res, equal_means = FALSE, equal_vars = FALSE) 
ggsave(p4, filename = here("output", "effect_unequal_mean_unequal_var.png"))

>>>>

n <- 10000
quantiles <- c(0.01, 0.025, seq(0.05, 0.95, by = 0.05), 0.975, 0.99)
rerun_simulation <- FALSE

@@

p1 <- plot_multiple(res, equal_means = TRUE, equal_vars = TRUE) 
ggsave(p1, filename = here("output", "figures", "effect_equal_mean_equal_var.png"))

p2 <- plot_multiple(res, equal_means = FALSE, equal_vars = TRUE) 
ggsave(p2, filename = here("output", "figures", "effect_unequal_mean_equal_var.png"))

p3 <- plot_multiple(res, equal_means = TRUE, equal_vars = FALSE) 
ggsave(p3, filename = here("output", "figures", "effect_equal_mean_unequal_var.png"))

p4 <- plot_multiple(res, equal_means = FALSE, equal_vars = FALSE) 
ggsave(p4, filename = here("output", "figures", "effect_unequal_mean_unequal_var.png"))
